Supporting Information\\ \textit{Cross Validation Approaches for Penalized Cox Regression}

### 2023-08-11 main.tex
update table 3 and upload new R code

\begin{table}[ht]
\centering
\caption{\label{tb:shedden} The C Index and Brier Score of all elastic net models selected by cross-validation methods }
\begin{tabular}{lccccc}
\hline
  & \multicolumn{5}{c}{Cross-validated C Index} \\ 
  & $\alpha = 0.3$ & $\alpha = 0.5$ & $\alpha = 0.7$ & $\alpha = 0.9$ & $\alpha = 1$ \\ \cline{2-6}
V \& VH      & 0.639 & 0.637 & 0.638 & 0.637 & 0.637\\
Basic       & 0.647 & 0.639 & 0.638 & 0.638 & 0.639 \\
Linear Pred    & \textbf{0.650} & 0.647 & 0.638 & 0.638 & 0.639  \\
Deviance Resid & 0.645 & 0.637 & 0.638 & 0.637 & 0.637 \\ 
\addlinespace
  & \multicolumn{5}{c}{Brier Score} \\ 
  & $\alpha = 0.3$ & $\alpha = 0.5$ & $\alpha = 0.7$ & $\alpha = 0.9$ & $\alpha = 1$ \\ \cline{2-6}
V \& VH  & 0.243 & 0.244 & 0.244 & 0.245 & 0.245 \\
Basic  & 0.233 & 0.243 & 0.244 & 0.244 & 0.244 \\
Linear Pred & \textbf{0.229} & 0.232 & 0.244 & 0.244 & 0.244 \\
Deviance Resid & 0.235 & 0.244 & 0.244 & 0.245 & 0.245 \\ 
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\centering
\caption{\label{tb:shedden} The C Index and Brier Score of all elastic net models selected by cross-validation methods }
\begin{tabular}{lcccccccc}
\hline
  & \multicolumn{8}{c}{Cross-validated C Index} \\ 
  & $\alpha = 0.05$ & $\alpha = 0.1$ & $\alpha = 0.2$ & $\alpha = 0.3$ & $\alpha = 0.5$ & $\alpha = 0.7$ & $\alpha = 0.9$ & $\alpha = 1$ \\ \cline{2-9}
V \& VH     & 0.645 &0.645 &0.643 &0.630 &0.626 &0.617 &0.617 &0.617\\
Basic       &0.652 &0.649 &0.650 &0.650 &0.649 &0.650 &0.651 &0.651 \\
Linear Pred    &0.649 &0.648 &0.650 &0.650 &0.649 &0.648 &0.617 &0.617  \\
Deviance Resid &0.648 &0.645 &0.647 &0.646 &0.626 &0.617 &0.617 &0.617 \\ 
\addlinespace
  & \multicolumn{8}{c}{Brier Score} \\ 
  & $\alpha = 0.05$ & $\alpha = 0.1$ & $\alpha = 0.2$ & $\alpha = 0.3$ & $\alpha = 0.5$ & $\alpha = 0.7$ & $\alpha = 0.9$ & $\alpha = 1$ \\ \cline{2-9}
V \& VH &0.232 &0.231 &0.232 &0.243 &0.245 &0.249 &0.249 &0.249 \\
Basic  &0.221 &0.226 &0.226 &0.225 &0.224 &0.221 &0.221 &0.221 \\
Linear Pred & 0.220 &0.228 &0.226 &0.225 &0.224 &0.224 &0.249 &0.249 \\
Deviance Resid &0.229 &0.231 &0.229 &0.228 &0.245 &0.249 &0.249 &0.249 \\ 
\hline
\end{tabular}
\end{table}
